Beyond Adaptive Web Design

### 2014-03-17 paper/paper.tex
feat: experiment using voice commands

Speech input provides a great opportunity to take a complete control over web application using only voice commands. For this purpose we have used web browser's Speech API for continuous speech recognition and built a configurable and reusable module. Speech recognition is however currently possible online only.

@@

But there are much more interesting things we can achieve using speech input. We can even use multiple languages for speech recognition. One of the biggest problems of the voice commands is however incorrect speech recognition. To solve this issue we can conditionalize regular expressions or use utterance error correction.

>>>>

Speech input provides a great opportunity to take a complete control over web application using only voice commands. For this purpose we have used web browser's Speech API for continuous speech recognition and built a configurable and reusable module. Speech recognition is however currently an experimental feauture and is possible online only.

@@

We have created an experiment based on our module which provides control over to-do list. There were 7 voice commands using exact expressions and 9 using regular expressions. But there are much more interesting things we can achieve using speech input. We can even use multiple languages for speech recognition. One of the biggest problems of the voice commands is however incorrect speech recognition. To solve this issue we can conditionalize regular expressions or use utterance error correction.
